\subsection{Video Games and Machine Learning}\label{sec:mlandonlinevideogames}
In video games, one or more players make a number of choices trying to win. The choices made by a single player can be seen as a strategy. The state space of video games can be so enormous that it is impossible to comprehend for a human, which means decisions not optimal for winning, may be made. For such video games, machine learning techniques may be able to either outperform human players or provide them valuable support for their decisions.

Machine learning has already been applied to various games H.\ Park et al.\ applied scouting algorithms and various machine learning techniques to predict early game strategy in StarCraft~\cite{Park:2012:PES:2425296.2425298}. J.\ Mullen et al.\ applied several machine learning techniques to develop an agent that successfully played Super Mario Bros.~\cite{supermario}. For Dota 2, which is a video game very similar to LoL.\@, K.\ Conley and D.\ Perry have trained a classifier to predict the winning team of a Dota 2 match~\cite{dota2article}, by only considering the heroes chosen at the beginning of the game. The classifier can assist players in picking a good combination of heroes. Each feature used, represents the presence or absence of a particular hero on one of the teams.When training on 18,000 matches they reached an accuracy of 69.8\% on the 5,669 matches in their test set. With 50,000 training samples, they almost reached 70\% accuracy. Only matches between players of similar skill levels were considered.

% RELATED WORK ABOUT DISTRIBUTED FILE SYSTEMS AND COMPUTATION
%Konstantin Shvachko, et al.\, created \emph{Hadoop distributed file system} (HDFS), to reliably handle very large data and to stream that data to user application at high %bandwidth. They described the architecture and showed that it can successfully handle 25PB of Yahoo enterprise data~\cite{HDFS}.
%Avinash Lakshman and Prashant Malik created an alternative to Hadoop called Cassandra, which uses Amazon's Dynamo scheme~\cite{ApacheCassandra}.
%Vinod Kumar Vavilapalli et al.\ expanded on Hadoop with YARN, which decoupled the programming model from the resource management infrastructure, it also delegates many of the %scheduling functions to per-application components~\cite{ApacheHadoopYARN}.
%
%Hadoop MapReduce and different variants have successfully been used for big data problems, by distributing the work load between many node in a cluster~\cite{DeanMapReduce}. 
%
%Matei Zaharia, et al.\ have created Apache Spark and using this framework, the computation time is reduced if the data is being reused, in e.g.\ iterative machine learning or 
%iterative data analysis tools~\cite{ApacheSpark}.



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
